NIRCam Calibration Plan

### 2016-11-23 ms.tex
I put in an acknowledgement to psynphot.
I added the 5 transfer plan George and I discussed to go from direct bright calibrators to faint ones.

\usepackage{natbib}
\bibliographystyle{astroads}

@@

The James Webb Space Telescope \citep[JWST; e.g.][]{gardner2006SSRv} will need absolute calibration.

\section{Pan-Starrs Photometry}

We obtained $grizy$ Pan-Starrs photometry for all three clusters \citep{magnier2013photLadder,schlafly2012photcal,tonry2012panstarrsPhot}.

@@

\section{Ways to Observe Really Bright Stars With NIRCam}

@@

>>>>

\usepackage{natbib}
%\usepackage{pdflscape}
\bibliographystyle{astroads}

@@

The James Webb Space Telescope \citep[JWST; e.g.][]{gardner2006SSRv} will need absolute calibration for many of its science goals.

\section{Photometry}

We obtained $grizy$ Pan-Starrs photometry for all three clusters \citep{magnier2013photLadder,schlafly2012photcal,tonry2012panstarrsPhot}.
We also looked up the $g$ - $r$ colors

@@

\section{Transferring to Directly Calibrated Sources}

In addition to observing the primary JWST standards for absolute calibration, it will be possible to observe stars with direct calibration.

\begin{table}
\centering
\caption{Direct Calibrated Source to Deep Calibrator}\label{tab:clusterProp}
\begin{tabular}{lrrrrrr}
\hline \hline
Step		& Source						& Spectral Type	& K Mag		& ND Filter		& Subarray	& Filter \\
\hline \hline
1		& Direct Calibrator\tablenotemark{a}	& G2 V 			& -1.49		& On	&	32$\times$32	& F466N	\\
2		& Medium Calibrator				& G2 V			& 6  			& On  &	32$\times$32	& F466N    \\
3		& Medium Calibrator				& G2 V			& 6  			& Off &	32$\times$32	& F466N    \\
4		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	& F466N    \\
5		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	& F444W    \\
6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Array  	& F444W    \\
%         &                                      & 
%
%Parameter  				&  Step 1			& Step 2			& Step 3			& Step 4 			& Step 5		& Step 6 \\
%\hline \hline
%Source					& Direct Calibrator\tablenotemark{a}	& Medium Calibrator	& Medium Calibrator	& Faint Cluster Star	& Faint Cluster Star & Faint Cluster Star\\
%Spectral Type				& G2 V			& G2 V			& G2 V			& G2 V			& G2 V	& G2 V \\
%K magnitude				& -1.49			& 6				& 6				& 16				& 16		& 16 \\
%Neutral Density Filter			& On				& On				& Off				& Off				& Off		& Off\\
%Subbarray					& 32$\times$32		& 32$\times$32		& 32$\times$32		& 32$\times$32		& 32$\times$32	& Full Frame \\
%Filter						& F466N			& F466N			& F466N			& F466 N			& F444W 	& F444W\\
\hline
\end{tabular}
\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, $\alpha$ Cen	 A or Vega.}
\end{table}

\subsection{Ways to Observe Really Bright Stars With NIRCam}

@@

Sensitivity and saturation limits make use of \texttt{pysynphot} \citep{lim2015pysynphot} with Phoenix stellar models \citep{allard2012phoenix} ranging from 4.0 to 5.0 in log(g).
